Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2022-12-30 Manuscript/SupMaterial.Rmd
Added Gamma parameters
Submitted version

---
title: Supplementary Material for 'New insights into the Weddell Sea ecosystem applying
  a network approach'
author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
bibliography: ../WeddellSea.bib
output:
  pdf_document: default
  word_document: default
---

@@

The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions. Table 3 shows the results for the six candidate models used.

>>>>

---
title: Supplementary Material for 'New insights into the Weddell Sea ecosystem applying
  a quantitative network approach'
author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
bibliography: ../WeddellSea.bib
output:
  pdf_document: default
  word_document: default
---

@@

The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions. Gamma parameters are: shape = 2.699e-1 and scale = 2.008e+4. Table 3 shows the results for the six candidate models used.
